---
title: "Two Months of Pool Practice"
date: 2026-09-26
categories: [R, Pool, Personal]
---

## Getting Back to Pool

After finishing my undergraduate courses, I had about two months of free time. I started playing pool more regularly again.

I was curious whether spending more time practicing each week would be related to how I performed in my weekly games. I created a small dataset representing eight weeks of practice and competition results.

```{r}
pool_data <- data.frame(
  week = 1:8,
  practice_hours = c(4, 6, 5, 8, 10, 7, 12, 11),
  matches_won = c(1, 2, 1, 3, 4, 3, 5, 4)
)

pool_data
```

## Practice Time

First, I looked at my average weekly practice time.

```{r}
mean(pool_data$practice_hours)
```

I also calculated the average number of matches won each week.

```{r}
mean(pool_data$matches_won)
```

## Practice and Competition Results

To see whether practice time and competition results moved together, I calculated their correlation.

```{r}
cor(pool_data$practice_hours, pool_data$matches_won)
```

A positive correlation would mean that weeks with more practice tended to also have better competition results.

## Visualizing the Relationship

```{r}
plot(
  pool_data$practice_hours,
  pool_data$matches_won,
  xlab = "Practice Hours per Week",
  ylab = "Matches Won",
  main = "Pool Practice and Weekly Results",
  pch = 19
)

abline(
  lm(matches_won ~ practice_hours, data = pool_data)
)
```

The plot suggests a positive relationship between practice time and matches won. In this small example, the weeks when I practiced more generally also had better results.

Of course, practice time is not the only thing that affects a pool match. Opponents, concentration, and how I played on that particular day could also matter.