---
title: "Two Months of Pool Practice"
author: "Kangju Sun"
date: 2026-09-26
categories: [R, Pool, Personal]
---

## Getting Back to Pool

After finishing my undergraduate courses, I had about two months of free time and started playing pool more regularly again.

I was curious whether spending more time practicing each week would be related to how I performed in my weekly games.

Data source: I created this small example dataset based on my pool-practice routine during that period. [View the data](pool_practice.csv).

```{r}
pool_data <- read.csv("pool_practice.csv")
pool_data
```

## Practice Time

First, I looked at my average weekly practice time.

```{r}
mean(pool_data$practice_hours)
```

I also calculated the average number of matches won each week.

```{r}
mean(pool_data$matches_won)
```

## Practice and Competition Results

To see whether practice time and competition results moved together, I calculated their correlation.

```{r}
cor(pool_data$practice_hours, pool_data$matches_won)
```

The correlation is positive, so in this small dataset, weeks with more practice generally also had better competition results.

## Visualizing the Relationship

```{r}
#| label: fig-pool-practice
#| fig-cap: "Weekly pool practice time and matches won"

plot(
  pool_data$practice_hours,
  pool_data$matches_won,
  xlab = "Practice Hours per Week",
  ylab = "Matches Won",
  main = "Pool Practice and Weekly Results",
  pch = 19
)

abline(
  lm(matches_won ~ practice_hours, data = pool_data)
)
```

The plot also suggests a positive relationship between practice time and matches won.

Of course, practice time is not the only thing that affects a pool match. Opponents, concentration, and how I played on that particular day could also matter.

## AI Use

I used [ChatGPT](https://chatgpt.com/) to help troubleshoot code and review the wording and structure of this post. I reviewed and tested the final code and content myself.
